---
title: "Analysis of coronavirus misinformation"
author: "nancy"
date: "2024-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readr)

misinfo_d <- read_csv('../life-under-lockdown-wave2-extract.csv')
```

```{r}
misinfo_d %>%
  ggplot(aes(x=beliefs)) +
  geom_histogram(bins=6)
```
```{r}
mean(misinfo_d$beliefs)
```
##use t test to check whether  a difference in the sample is likely to reflect a difference in the population

```{r}
misinfo_d %>%
  filter(gender %in% c('Female','Male'))%>%
  t.test(formula = beliefs ~ gender, data = .)
```
##p-value = 0.2303 it tells us how strong the our evidence  is for rejecting the null hypothesis
##if we assume that in the population there is no difference in the number of misinformation beliefs between men and women. we take a random sample of 500, there's a 23% chance that we will get a difference this big between the two, even though there is no difference in the population if you take 4 random samples of 500 or 498. if you take 4 random samples of 498 from a population in which there is no difference between the genders.
## p-value = 0.2303 it tells us how strong the our evidence  is for rejecting the null hypothesis
## if we assume that in the population there is no difference in the number of misinformation beliefs between men and women. we take a random sample of 500, there's a 23% chance that we will get a difference this big between the two, even though there is no difference in the population if you take 4 random samples of 500 or 498. if you take 4 random samples of 498 from a population in which there is no difference between the genders.

In the sample, males had more misinformation beliefs (M = 0.73) than females (M = 0.61), but this was not statistically significant, t(494.31) = -1.201, p = 0.230.
# in the sample, males had more misinformation beliefs (M = 0.73) than females (M = 0.61), but this was not statistically significant, t(494.31) = -1.201, p = 0.230.


